\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2019-05-17 paper/manuscript_paNote.tex
new results
highlighted changes in the results

The results are shown in Table \ref{tabSTMtopwords60}. Many of the topics associated with Democrats fit with what we understand to be national party priorities. Topic 21, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters. Similarly, employee rights are represented in Topic 47. Democrats also exhibit a strong preference for words related to public finances, such as Topic 32 ('budget', 'revenue', 'expenditure') as well as Topic 19 ('debt', 'bond', 'financial'). We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money. This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending. A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 55 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{tabSTMtopwords120_1} and \ref{tabSTMtopwords120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement. On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}. On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on the police, even after controlling for crime \citep{Einstein2015}. Finally, Democrats also focus more on the deliberative process of policymaking, as topics 31 ('agenda', 'committee'), 34 ( `comment', `draft', `feedback'), 48 (`absent', `aye', `nay'), and 37 ('audit', 'procedure', 'oversight') attest to.  This openness regarding the policy process on behalf of cities with Democratic mayors fits with the findings of \citet{grimmelikhuijsen2012developing}, which are that left-wing local governments exhibit greater transparency via website content.

City websites with Republican mayors, meanwhile, exhibit a pronounced focus on the essential functions of government. Basic utilities such as energy (Topic 7), fire protection (Topic 17), drinking water (53), and garbage removal (Topic 49) are included among those topics that are more prevalent in cities with Democratic mayors. Similarly, protecting citizens from natural disasters is a focus in topics 1 ('storm', 'runoff', 'drainage') and 42 ('breastfeed', 'infection', 'mosquito' -- and so, essentially, about the Zika virus), which may reflect the greater prevalence of Republican mayors in the southeast, a region which is more often affected by hurricanes and tropical diseases.

@@

\input{tables/stmTopWords60.tex} %\ref{tabSTMtopwords2}
\input{tables/stmTopWords60New.tex}

>>>>

The results are shown in Table \ref{tabSTMtopwords60}. Many of the topics associated with Democrats fit with what we understand to be national party priorities. Topic \textbf{52}, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters. Similarly, employee rights are represented in topics \textbf{10} and \textbf{29} \textbf{[DEBATABLE]}. Democrats also exhibit a strong preference for words related to public finances, such as Topic \textbf{58} ('budget', 'revenue', 'expenditure'), \textbf{topic 45 ('asset', 'actuarial', 'liability', 'financial')}, \textbf{topic 35 ('bond', 'obligation', 'proceeds')} as well as \textbf{topic 55 ('taxable', 'deed', 'value')}. We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money. This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending. A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, \textbf{59} ('burglary', 'robbery', 'theft', 'homicide') depicts Democrats' complicated relationship with law enforcement \textbf{[This used to be about police as well, but now it's more of a crime topic]}. On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}. On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on the police, even after controlling for crime \citep{Einstein2015}. Finally, Democrats also focus more on the deliberative process of policymaking, as \underline{topics 31 ('agenda', 'committee') \textbf{[This is now the second-most REPUBLICAN topic 46]}}, \underline{34 (`comment', `draft', `feedback') \textbf{[This is now REPUBLICAN topic 5]}}, \textbf{1} (`absent', `preside', `authorized'), and \textbf{4} ('audit', 'procedure', 'oversight') attest to. \textbf{[Republicans also have topic 16]}  This openness regarding the policy process on behalf of cities with Democratic mayors fits with the findings of \citet{grimmelikhuijsen2012developing}, which are that left-wing local governments exhibit greater transparency via website content.

City websites with Republican mayors, meanwhile, exhibit a pronounced focus on the essential functions of government. Basic utilities such as energy (Topic \textbf{20}), fire protection (Topic \textbf{51} \textbf{[This topic has changed a lot.]}), \underline{drinking water (53) \textbf{[topic missing]}}, and \underline{garbage removal (Topic 49) \textbf{[topic missing]}} are included among those topics that are more prevalent in cities with Democratic mayors. Similarly, protecting citizens from natural disasters is a focus in \underline{topics 1 ('storm', 'runoff', 'drainage') \textbf{[topic missing]}} and \textbf{2} ('influenza', 'infection', 'vaccine' \textbf{[This is not about Zika anymore, but infectious diseases in general.]}), which may reflect the greater prevalence of Republican mayors in the southeast, a region which is more often affected by hurricanes and tropical diseases.

@@

\input{tables/stmTopWords60.tex}
\input{tables/stmTopWords60_OLD.tex} %\ref{tabSTMtopwords2}
